\TheTitle

### 2017-06-12 paper/abstract.tex
Resizing text width
84-wide text doesn't fit split-screen on my little monitor.
Resizing it down to 72-wide.

Natively, git uses a directed acyclic grph mode (DAG) with references pointing from
the (TODO: most recent commit?, it's not the HEAD because that moves around) toward
the initial commit in the repository. This model is useful and necessary to the
internal functionality of the version control system, but does not provide users
with a clear nderstand of the events occuring in the repository. Due to the
direction of the link in the DAG, visualziation tools, like gitk, are unable to
provide summarized aggregation of the commits at a given merge. Furthermore, the
visual DAG does not provide a clear explanation of the events taking place in the
repository.

@@

% \evan{Change this when we get the actual results, this is from the pilot study} We
% find that although the DAG view used by Gitk provides more information about the
% repository, in many cases it povides too much information and overwhelms the user.

% \evan{Move this}
% In some cases, where the structure of the merge tree is flat, that is to say that it
% has no inner merges, users are able to easily determine which commits are merged
% together, but are unable to determine which merge is the final merge is the root of
% the tree.

>>>>

Natively, git uses a directed acyclic graph model (DAG) with references
pointing from the most recent commit (TODO: most recent commit?, it's
not the \emph{HEAD} because that moves around) toward the initial commit
in the repository. This model is useful and necessary to the internal
functionality of the version control system, but does not provide users
with a clear nderstand of the events occuring in the repository. Due to
the direction of the link in the DAG, visualziation tools, like gitk,
are unable to provide summarized aggregation of the commits at a given
merge.  Furthermore, the visual DAG does not provide a clear explanation
of the events taking place in the repository.

@@

% \evan{Change this when we get the actual results, this is from the
% pilot study} We find that although the DAG view used by Gitk provides
% more information about the repository, in many cases it povides too
% much information and overwhelms the user.

% \evan{Move this} In some cases, where the structure of the merge tree
% is flat, that is to say that it has no inner merges, users are able to
% easily determine which commits are merged together, but are unable to
% determine which merge is the final merge is the root of the tree.

### 2017-06-12 paper/introduction.tex
Resizing text width
84-wide text doesn't fit split-screen on my little monitor.
Resizing it down to 72-wide.

Merge-trees, as presented by Wilde and German\cite{Wilde2016}, are a data structure
designed to make the navigation and summarization of git merges simpler than using
the directed acyclic graph (DAG), as done in gitk among other tools\evan{does this
  need a citation?}. Git uses the DAG model internally, making it simple to
construct tools directly on the DAG;\@ however, this model does not provide a clear
summarization of the events occuring in the repository. Gitk and the git command
line interface (cli) both provide the user with a visualization of the DAG of the
repository.

>>>>

Merge-trees, as presented by Wilde and German\cite{Wilde2016}, are a
data structure designed to make the navigation and summarization of git
merges simpler than using the directed acyclic graph (DAG), as done in
gitk among other tools\evan{does this need a citation?}. Git uses the
DAG model internally, making it simple to construct visualization tools
directly using the DAG of the repository;\@ however, this model does not
provide a clear summarization of the events occuring in the repository.
Gitk and the git command line interface (cli) both provide the user with
a visualization of the DAG of the repository.

Merge-trees have two primary issues; first, the merge-tree model has not
been evaulated, and cannot therefor claim to simplify the summarization
and navigation tasks. Second, merge-trees have only been implemented for
the Linux repository, which follows a strict merge-policy where only
Linus can merge into the master branch.

The contributions of this paper tackle both of these issues. We perform
a user-study, to verify that the merge-tree model is able to improve the
accuracy and speed of summarization tasks. Second, we generalize the
algorithm, creating an upper bound on the number of commits visisted in
the construction of the merge-trees.

\subsection{Merge-Trees}
\label{sub:merge_trees}

Internally, git uses a DAG as the primary data structure for managing
commits in a repository. An individual commit will have an ordered list
of parents, where the parent in the first position is on the same branch
as the commit, and the other parents are in the same order as they were
merged. In the event that a merge commit contains a list of parents with
more than two parents, this merge is an octopus merge. The commits may
be divided into two groups, commits with only a single parent, and
commits with at least two commits. Commits with with many parents are
merge commits, combining the effects of potentially many individual
commits.
